cardinalR: Generating interesting high-dimensional data structures

### 2025-03-30 paper-cardinalR.Rmd
Paper's initial workflow

```{r setup, include=FALSE}
options(repos = "https://cloud.r-project.org") ## set up CRAN mirror
knitr::opts_chunk$set(
  cache=FALSE, 
  message=FALSE, 
  warning=FALSE,
  out.width = "100%")

@@

```{r load-libraries}

@@

# Background

# Methods

>>>>

```{r setup, include=FALSE}
options(repos = "https://cloud.r-project.org") ## set up CRAN mirror
knitr::opts_chunk$set(
  echo = FALSE,
  cache=FALSE, 
  message=FALSE, 
  warning=FALSE,
  out.width = "100%")

@@

```{r load-libraries}
library(tidyverse)
library(knitr)
```

@@

# Implementation

## Installation

The package can be installed from CRAN using

> ```install.packages("cardinalR")```

and from GitHub using

> ```remotes::install_github("jayanilakshika/cardinalR")```

to install the development version.

## Web site

More documentation of the package can be found at the web site https://jayanilakshika.github.io/cardinalR/.

## Data sets

The `cardinalR` package comes with several data sets that load with the package. These are described in Table `r knitr::asis_output(ifelse(knitr::is_html_output(), '\\@ref(tab:datasets-tb-html)', '\\@ref(tab:datasets-tb-pdf)'))`.

```{r}
datasets_tb <- tibble(dt = c("mobius_clust_data", 
                             "mobius_clust_tsne_param1", 
                             "mobius_clust_tsne_param2",
                             "mobius_clust_tsne_param3",
                             "mobius_clust_umap_param1",
                             "mobius_clust_umap_param2",
                             "mobius_clust_umap_param3"), 
                      text = c("",
                               "", 
                               "",
                               "",
                               "",
                               "", ""))
```

```{r datasets-tb-html, eval=is_html_output()}
datasets_tb |> 
  kable(caption = "cardinalR data sets", col.names = c("data", "explanation")) 
```

```{r datasets-tb-pdf, eval=is_latex_output()}
datasets_tb |> 
  kable(caption = "cardinalR data sets", format="latex", col.names = c("data", "explanation"), booktabs = T)  |>
  column_spec(1, width = "4cm") |>
  column_spec(2, width = "8cm")
```

## Functions
